On The Impact of Atoms of Confusion in JavaScript Code

### 2021-05-03 6_Conclusion.tex
final review

%As mentioned, the results of the interviews
The results of the interviews pointed out additional JavaScript constructs and idioms
that might introduce misunderstanding. These include not only nested callbacks and prototype-based
inheritance (which might not have a counterpart version), but also idioms such
as \emph{property access} and \emph{arrow functions}. As future work, we intend to
reproduce our study to validate whether or not these \emph{atom candidates} affect
the understanding of JavaScript code.

>>>>

%As mentioned, the results of the interviews
The results of the interviews pointed out additional JavaScript constructs and idioms
that might introduce misunderstanding. These include not only nested callbacks and prototype-based
inheritance (which might not have a counterpart version), but also idioms such
as \emph{property access} and \emph{arrow functions}. As future work, we intend to
reproduce our survey to validate whether or not these additional
\emph{atom candidates}, which the interviewees pointed out, truly affect
the understanding of JavaScript code.
